### 2017-10-26 Risk analysis/Text/Layout/Layout/chapter2_methods.tex
Writing hydrocarbon system part, progress!

        \subsection{Economic significance and reservoir valuation}\label{sec:Reservoir_values}
        In this work, the generated structural models are to be assigned an economic significance in order to approach a real setting, in which hypothetical actors could have an interest in taking a decision, and thus, to evaluate the influence of the Bayesian inference of the decision-making process. Changes in Bayes actions are considered as a measure for this effect.      For this purpose, it is assumed that a hydrocarbon reservoir system is represented by each geological model realization.

        \subsubsection{Reservoirs and structural hydrocarbon traps}
        Such hydrocarbon are typically comprised of:
        \begin{enumerate}
        	\item
        \end{enumerate} \citep{dolson2016basics}
        These are typically comprised stratigraphically of at least one potential reservoir formation, succeeded by at least one sealing layer above. Additionally, a trapping mechanism is normally required (source?).\\
        The resulting reservoirs are to be valuated in a way that respective estimations on the basis of loss functions can be conducted, i.e. Bayesian decision theory is applicable. In the typical petroleum industrial setting, the main question is one of how much of the resource can be produced and how high the return on investment will be \citep{dean2007volumetric}.

        \subsubsection{Original oil-in-place and recoverable volumes as value measures}

>>>>

        \section{Model evaluation: Economic significance and reservoir valuation}\label{sec:Reservoir_values}
        In this work, the generated structural models are to be assigned an economic significance in order to approach a real setting, in which hypothetical actors could have an interest in taking a decision, and thus, to evaluate the influence of the Bayesian inference of the decision-making process. Changes in Bayes actions are considered as a measure for this effect. For this purpose, it is assumed that a hydrocarbon reservoir system is represented by each geological model realization.

        \subsection{Hydrocarbon reservoir system and structural traps}
        Such hydrocarbon systems are typically comprised of:
        \begin{enumerate}
        	\item A kerogen-rich \textbf{source rock} which produced and emitted hydrocarbons during its burial history, given sufficient heating \citep{dolson2016basics} These are typically organic-rich sedimentary rocks, shales in particular. For the purpose of this work, it is assumed that a  suitable source rock is present and hydrocarbons expulsion took place after the formation of any trap-defining structures in our geological models.
        	\item A \textbf{pathway} that allows expelled oil and gas to migrate upwards through the subsurface from the source rock into potential reservoir formations \citep{dolson2016basics}. This condition is also assumed to be given in our model. Basement formations in the geological model are simply defined as permeable.
        	\item \textbf{Seal} formations that are able to halt hydrocarbons on their migration pathway. Such sealing is generally defined by a reduction of pore space geometry relative to migration energy. Lithologically, seals are most commonly comprised of shales, siltstones, tight carbonates, evaporites and salts. Sealing is thus defined primarily by changes in stratigraphical composition to low porosities and micro-sized pore throats, which are characterized by a high capillary entry pressure \citep{dolson2016basics, dolson2016quantifying}. An additional factor to sealing is posed by the presence of faults. Fault zones may possess significantly higher or lower permeabilities then surrounding rock formations which means that they may serve as fluid flow conduits or migration barriers or respectively \citep{van2003lateral, sorkhabi2005place}. The possible influence of faults on structural hydrocarbon traps is elaborated in further detail below. For the model in this work, the reservoir cap rock is assumed to be a shale.
        	\item Suitable \textbf{reservoir formations}, in which these hydrocarbons volumes can be stored. For this, a suitable percentage of void space in a rock formation, i.e. a sufficiently high porosity, is required. A second significant factor is the connectivity of the porosity through pore throats. The larger the pore throats, the easier it is for fluids to migrate in a rock. Typical reservoir rocks are sandstones and carbonates, but even normally tight lithologies might serve as reservoirs, if they are fractured \citep{dolson2016basics}. In the models of this work, reservoir formations are assumed to be conventional sandstones.
        \end{enumerate}
        Given the migration and a combination of appropriate reservoir-seal sequence geometries, many different types of traps, in which hydrocarbons can accumulate, are possible. A common trap type is a structural four-way closure, i.e. as reservoir-seal system that was folded into closed anticlines, often resembling a dome and is thus predominantly defined by the structural closure relief and the cap rock sealing capacity. Such a trap type can be considered to be closed, as the reservoir surface contours are closed in a circle or oval around a relief high. Closure can also defined by any other intersection of a contour with a seal. The point at which a a contour fails to close is referred to as spill point \citep{dolson2016basics}.

        In this work, reservoir systems and traps resulting from modeling are to be valuated in a way that respective estimations on the basis of loss functions can be conducted, i.e. Bayesian decision theory is applicable. In the typical petroleum industrial setting, the main question is one of how much of the resource can be produced and how high the return on investment will be \citep{dean2007volumetric}.

        \subsection{Original oil-in-place and recoverable volumes as value measures}
